### 2020-01-16 paper/sex_selection_spacing-ver3.tex
Continue editing fertility discussion

To predict cohort fertility based on the models above, I estimate the probability of 
progression to the next parity for each spell.
I include the spell from marriage to first birth, even those results are not examined 
above because of the problems with capturing the exact timing of marriages for the first 
two rounds of the survey.
The estimated progression probabilities should, however, be less affected by this
problem.
To ensure that the predictions depend solely on sample composition and the estimate, I
use the age at marriage for each woman and predict the likelihood of progressing to
each parity, assuming two years increases in age between each parity.
Hence, for a woman married at age 20, I use age 22 for predicting progression 
to the second birth, 24 for the third, and 26 for the fourth.

The parity progression depends on the sex composition for prior children for
parity two and above.
For example, the likelihood of a second birth is the probability of having a first birth 
multiplied with
sum of the 
probability of having a son as the first child conditional on having a first child 
multiplied with parity progression probability if the first child is a son 
and the 
probability of having a girl as the first child  conditional on having a first child
multiplied with the parity progression probability if the first child is a girl.
$$
prob(2nd) = prob(1st) * (prob(son|1st)*prob(2nd|son) + prob(girl|1st) * prob(2nd|girl)
$$

The survey rounds do not coincide entirely with the periods I use for the model.
For the NFHS-4, I use the model results for the 2005--2016 period, 
for NFHS-3 the 1995-2004, NFHS-2 1985-1994, and for NFHS-1 1972-1984.

The predicted fertility using the hazard model assumes that women in the sample
follows the parity progression probability based on the given period. 
For example, for the NFHS-4 the predictions assume that the women in the sample follow
the estimated behavior for all four spells based on the 2005--2016 sample.

@@

Consistent with the rapid increase in the use of sex selection from the mid-eighties
the most substantial differences between the two fertility measures are for higher
educated women for earlier samples.

>>>>

To predict cohort fertility based on the models above, I estimate the probability of 
progression to the next parity for each spell.
I include the spell from marriage to first birth, even those results are not examined 
above because of the problems with capturing the exact timing of marriages for the first 
two rounds of the survey.
The estimated progression probabilities should, however, be less affected by this
problem.

To ensure that the predictions depend solely on sample composition and the estimate, I
use the age at marriage for each woman and predict the likelihood of progressing to
each parity, assuming three years increases in age between each parity.
Hence, for a woman married at age 20, I use age 23 for predicting progression 
to the second birth, 26 for the third, and 29 for the fourth.
[TK Predicted fertility is higher the younger the women and the shorter the assumed spacing?]

As shown above, the parity progression depends critically on the sex composition for prior 
children for parity two and above.
I, therefore, estimate the progression probability for each possible sex composition
and weigh those probabilities with the likelihood that they will occur based on the
prior spells.

The survey rounds do not coincide entirely with the periods I use for the hazard model.
For the NFHS-4, I use the model results for the 2005--2016 period, 
for NFHS-3 the 1995--2004 period, 
for NFHS-2 the 1985--1994 period, 
and for NFHS-1 the 1972--1984 period.
Because of the small number of women who had the highest level of education in the
1972--1984 period, I do not present a predicted fertility for this case.

The predicted fertility using the hazard model assumes that women in the sample
follows the parity progression probability in the period. 
For example, for the NFHS-4 the predictions I assume that all women in the sample follow
the estimated behavior for all four spells based on the 2005--2016 results.

@@

[some TFRs are actually going up!]

[CAVEAT: only first four births, these predicted fertility numbers likely too low,
especially for the lower education groups]
